---
title: "Export prediction as a raster GIS file"
author: "Facundo Muñoz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Export prediction as a raster GIS file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, message = FALSE}
library(geoRcb)  # cost-based kriging
require(sp)      # spatial classes
require(raster)  # rasterize
require(rgdal)   # input/output, projections
```

# Produce a kriging prediction

For the sake of the example, we are going to use the `noise` data, included with `geoRcb`.
First thing is to make it a `geodata` object, specifying the target variable.

```{r observations}
data(noise)
obs.gd <- as.geodata(obs, data.col="Leq")
```


Fit a cost-based variogram model and perform cost-based Kriging prediction.

```{r fit-model, message = FALSE}
vgmdl.dmat <- likfit(geodata = obs.gd,
                     ini = c(8,300),
                     cov.model = "matern",
                     dists.mat=dd.distmat)

KC <- krige.control(obj.model=vgmdl.dmat)
kp <- krige.conv(obs.gd,
                 locations=coordinates(loc),
                 krige=KC,
                 dd.dists.mat=dd.distmat,
                 dl.dists.mat=dl.distmat)
```


# Rasterize the prediction

```{r}
pred <- data.frame(coordinates(loc),
                   mean = kp$predict,
                   var = kp$krige.var)
coordinates(pred) <- 1:2    # Promote to SpatialPointsDataFrame
```

If the prediction locations (loc) formed a regular grid
we could inmediately promote to SpatialGridDataFrame
Then skip to Export

```{r make-gridded, eval = FALSE}
gridded(pred) <- TRUE   # not this case
```



Otherwise, then we need to create an "empty" grid at a specified
resolution, and then overlay the predicted values
It is possible to do it without resorting to package raster
but if find it much easier using it like this.

```{r}
resolution <- 10
prediction_grid <- raster(extent(loc), resolution = resolution)
prediction_grid <- rasterize(pred, prediction_grid, field = 'mean')
crs(prediction_grid) <- CRS(proj4string(loc))
prediction_grid <- as(prediction_grid, "SpatialGridDataFrame")
# plot(prediction_grid)
```


# Export

```{r}
fn <- tempfile()
writeGDAL(prediction_grid, fn)
```

